On the presentation of orthogonal groups over polynomial rings

### 2019-05-13 dl-paper.tex
Proved the last restricted axiom

Finally, suppose $g$ has type $5$.
Substituting in~\eqref{Z5} of~\cref{Zrels} $s = -\epsilon f$, $\xi = -\epsilon m$, $\eta=X$ and expressing $z_\alpha(f, mX)$ through other terms we obtain that
\begin{multline} \label{eq:zalpha} z_\alpha(f, mX) = x_{\alpha+\beta}(\epsilon Xf) \cdot x_{\beta}(-mX^2 f) \cdot x_{-\beta}(mf) \cdot x_\alpha(f) \cdot \\ 
 \cdot z_{\alpha+\beta}(-\epsilon X f, -\epsilon m) \cdot z_{-\beta}(-mf, -X) \cdot x_{-\alpha-\beta}(-\epsilon m^2X f) \cdot x_{-\alpha}(-m^2X^2 f), \end{multline}
and the latter expression is a product of generators of type 1, 1, 2, 5, 1, 2, 1, 4.
\end{proof}
For $m \in M$ denote by $P_\alpha(m)$ the coset $P_\alpha(0) \cdot x_{-\alpha}(mX)$.
From the above lemma it follows that $P_\alpha(*)$ coincides with the union of all $P_\alpha(m)$, $m\in M$. This allows us to make the following definition.

@@

\subsection{The subgroups $K(\alpha, \beta)$ and their properties}
Throughout this section $\alpha, \beta$ denote a fixed pair of roots of $\Phi$ forming a sharp angle (i.\,e. $\langle \alpha, \beta \rangle = 1$). We denote by $\Psi$ the subsystem of type $\rA_2$ generated by $\alpha$ and $\beta$.
\begin{df}
 Denote by $K(\alpha, \beta)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by the following elements:
 \begin{enumerate}
  \item $z_\gamma(Xf, \xi)$, for all $\gamma \in \Phi \setminus \Psi,$ and $x_{\alpha-\beta}(Xf)$, $x_{\beta-\alpha}(Xf)$;
  \item $x_{-\alpha}(X^2f)$, $x_{-\beta}(X^2f)$;
  \item $x_{\alpha}(Xf)$, $x_\beta(Xf)$;
  \item $c_{\pm \delta}(f, X\xi)$ for some fixed root $\delta \in \Phi \setminus \Psi$.
 \end{enumerate}
\end{df}

\begin{prop} \label{K-a-b}
 Every element $g \in K(A[X], M[X])$ can be written as a product $g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$ for some $m, m' \in M$ and $g_0 \in K(\alpha, \beta)$.
\end{prop}
\begin{proof}
 Denote by $\Sigma$ the special part of the parabolic subset $S = \Psi \cup \Phi^+$.
 Applying~\cref{thm:Stepanov} to $S$ we obtain that every element of $\St(\Phi, A[X], XM[X])$ can be presented as a product of 
  $z_\gamma(Xf, \xi)$, $\gamma \in \Sigma(S) \subseteq \Phi\setminus \Psi$ and $x_\gamma(Xf)$, $\gamma \in \Psi$.
 By~\cref{Kgen-strong} we can write $g$ as a product of these generators and generators of type 4.

@@

 Finally, after collecting terms $x_\epsilon(mX)$, $\epsilon \in \{ -\alpha, -\beta \}$ in the right-hand side of the resulting expression
  we obtain the desired decomposition for $g$. \end{proof}

It is clear from the definition that $K(\alpha, \beta) \subseteq P_\alpha(0) \cap P_\beta(0) \cap K(A[X], M[X])$.
The above proposition shows that this inlusion is, in fact, an equality.

\begin{lemma}
 The image of $K(\alpha, \beta)$ under $S_{\alpha}(a, -)$ is contained in the subgroup of $\St(\Phi, A[X, X^{-1}])$ 
 generated by $K(\alpha, \beta)$ and the subgroup $U$, which, by definition, is generated by $z_\gamma(f, X\xi)$, $\gamma \in Z_+(\alpha) \setminus \{ \alpha - \beta \}$.
 We call these elements generators of type 5.
\end{lemma}
\begin{proof}
By~\eqref{eq:Zconj1}, \eqref{eq:Zconj2} the conjugate to each generator $z_\gamma(Xf, \xi)$ of type 1 by $x_\alpha(aX^{-1})$ is a product of generators of type 5, 5, 1.
By~\eqref{eq:Zconj3} the conjugate to the generator $x_{-\alpha}(X^2f)$ is a product of generators of type 1, 5, 1, 2, 1, 1, 5, 5.
$S(\alpha, -)$ either fixes $x_{-\beta}(X^2f)$, the other generator of type 2, or transforms them into products of generators of type 2, 1.
Clearly, $S(\alpha, -)$ fixes both generators of type 3. 
As for the remaining generators type 4, \cref{Crels} shows that the corresponding conjugate can be written as a product of generators of type 5, 5, 4.
\end{proof}

\begin{corollary} If $\alpha$ and $\beta$ form a sharp angle, then the image of $K(\alpha, \beta)$ under $S(\alpha, -)$ is contained in $P_\beta(0)$. \end{corollary}
\begin{proof} Follows from the above lemma and the fact that the generators of $U$ are generators of the second type for $P_\beta(0)$ in the sense of~\cref{defP0}.
 Indeed, if $\gamma \in Z_+(\alpha) \setminus \{ \alpha - \beta \}$ is such that $\langle \beta, \gamma \rangle = -1$, then $ \langle \alpha - \beta, \gamma \rangle \geq 2$, hence
  $\gamma = \alpha - \beta$, a contradiction. \end{proof}

\begin{lemma} Suppose $\alpha$ and $\beta$ form a sharp angle, then $g \in K(A[X], M[X])$ then 
\[S_\alpha(a, g)\cdot  h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-N_{\alpha,-\beta}\cdot m'a) \in P\left(\beta, \frac{m'}{1 + am}\right).\] \end{lemma}
\begin{proof}
 By~\cref{K-a-b} $g = g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$ for some $g_0\in K(\alpha, \beta)$.
 \begin{multline} \nonumber S_\alpha(a, g) = S_\alpha(a, g_0) \cdot S(a, x_{-\alpha}(mX)) \cdot S_\alpha\left(\frac{a}{1+am}, x_{-\beta}(m'X)\right) = \\ = S_\alpha(a, g_0) \cdot \langle -a, m \rangle \cdot h_\alpha(1+am) \cdot x_{-\beta}(m'X) \cdot x_{\alpha-\beta}\left(\frac{N_{\alpha, -\beta} \cdot m'a}{1+am}\right) = \\ =
  S_\alpha(a, g_0) \cdot \langle -a, m \rangle \cdot  x_{-\beta}\left(\frac{m'X}{1+am}\right) \cdot x_{\alpha-\beta}\left(N_{\alpha, -\beta} \cdot m'a\right) \cdot h_\alpha(1+am). \end{multline}
The assertion now follows from the preceding corollary.
\end{proof}

\begin{lemma}
 If $\alpha$ and $\beta$ form a sharp angle then one has $K(\alpha, \beta)^{x_{\beta - \alpha}(a)} \subseteq P_\alpha(0)$ for $a \in A$.
\end{lemma}
\begin{proof}
 It is clear that $K(\alpha, \beta)^{x_{\beta - \alpha}(a)} \subseteq K(A[X], M[X]) \subseteq P_\alpha(*)$.
\end{proof}

>>>>

Finally, suppose $g$ has type $5$.
Substituting in~\eqref{Z5} of~\cref{Zrels} $s = -\epsilon f$, $\xi = -\epsilon m$, $\eta=X$ and expressing $z_\alpha(f, mX)$ through other terms we obtain that
\begin{multline} \label{eq:zalpha} z_\alpha(f, mX) = x_{\alpha+\beta}(\epsilon Xf) \cdot x_{\beta}(-mX^2 f) \cdot x_{-\beta}(mf) \cdot x_\alpha(f) \cdot \\ 
 \cdot z_{\alpha+\beta}(-\epsilon X f, -\epsilon m) \cdot z_{-\beta}(-mf, -X) \cdot x_{-\alpha-\beta}(-\epsilon m^2X f) \cdot x_{-\alpha}(-m^2X^2 f), \end{multline}
and the latter expression is a product of generators of type 1, 1, 2, 5, 1, 2, 1, 4.
\end{proof}

\begin{rem} \label{rem:palpha} From the above two lemmas it follows that the value of $p_\alpha$ on an element $g\in K(A[X], M[X])$ can be computed as follows. Express $g$ as a product of elements $z_{\beta}(Xf, \xi)$ for $\beta \in \Phi$ and $c_\delta(f, X\xi)$ for some fixed $\delta \perp \alpha$. Now $p_\alpha(g)$ coincides with the sum of constant terms of the polynomials $f$ corresponding to the factors of the form $z_{-\alpha}(Xf, \xi)$ occuring in this expression. \end{rem}

For $m \in M$ denote by $P_\alpha(m)$ the coset $P_\alpha(0) \cdot x_{-\alpha}(mX)$.
From the above lemma it follows that $P_\alpha(*)$ coincides with the union of all $P_\alpha(m)$, $m\in M$. This allows us to make the following definition.

@@

\subsection{The subgroups $K(\alpha, \beta)$ and their properties}
Throughout this subsection $\alpha, \beta$ denote a fixed pair of roots of $\Phi$ forming a sharp angle (i.\,e. $\langle \alpha, \beta \rangle = 1$). We denote by $\Psi$ the subsystem of type $\rA_2$ generated by $\alpha$ and $\beta$.
\begin{df}
 Denote by $K(\alpha, \beta)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by the following elements:
 \begin{enumerate}
  \item $z_\gamma(Xf, \xi)$, for all $\gamma \in \Phi \setminus \Psi$;
  \item $x_{-\alpha}(X^2f)$, $x_{-\beta}(X^2f)$;
  \item $x_{\alpha}(Xf)$, $x_\beta(Xf)$;
  \item $x_{\alpha-\beta}(Xf)$, $x_{\beta-\alpha}(Xf)$;
  \item $c_{\pm \delta}(f, X\xi)$ for some fixed root $\delta \in \Phi \setminus \Psi$.
 \end{enumerate}
\end{df}

\begin{prop} \label{K-a-b}
 Every element $g \in K(A[X], M[X])$ can be written as a product $g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$ for some $m, m' \in M$ and $g_0 \in K(\alpha, \beta)$. Consequently, $K(\alpha, \beta)$ coincides with the intersection $K(A[X], M[X]) \cap P_\alpha(0) \cap P_\beta(0)$.
\end{prop}
\begin{proof}
 Denote by $\Sigma$ the special part of the parabolic subset $S = \Psi \cup \Phi^+$.
 Applying~\cref{thm:Stepanov} to $S$ we obtain that every element of $\St(\Phi, A[X], XM[X])$ can be presented as a product of 
  $z_\gamma(Xf, \xi)$, $\gamma \in \Sigma(S) \subseteq \Phi\setminus \Psi$ and $x_\gamma(Xf)$, $\gamma \in \Psi$.
 By~\cref{Kgen-strong} we can write $g$ as a product of these generators and generators of type 4.

@@

 After collecting terms $x_\epsilon(mX)$, $\epsilon \in \{ -\alpha, -\beta \}$ in the right-hand side of the resulting expression
 we obtain the desired decomposition for $g$.

 It is clear from the definition that $K(\alpha, \beta) \subseteq P_\alpha(0) \cap P_\beta(0) \cap K(A[X], M[X])$. The reverse inclusion follows from the just proved decomposition and the fact that for $g\in K(A[X], M[X])$ by~\cref{rem:palpha} one has $p_{\alpha}(g) = m$ and $p_\beta(g) = m'$. \end{proof}

\begin{lemma} The image of $K(\alpha, \beta)$ under $S_{\alpha}(a, -)$ is contained in the subgroup of $\St(\Phi, A[X, X^{-1}])$ 
 generated by $K(\alpha, \beta)$ and the subgroup $U$, which, by definition, is generated by $z_\gamma(f, X\xi)$, $\gamma \in Z_+(\alpha) \setminus \{ \alpha - \beta \}$. We call these elements generators of type 6.
\end{lemma}
\begin{proof} By~\eqref{eq:Zconj1}, \eqref{eq:Zconj2} the conjugate to each generator $z_\gamma(Xf, \xi)$ of types 1 by $x_\alpha(aX^{-1})$ is a product of generators of type 6, 6, 1.
By~\eqref{eq:Zconj3} the conjugate to the generator $x_{-\alpha}(X^2f)$ is a product of generators of type 1, 6, 1, 2, 1, 1, 6, 6.
Clearly, $S(\alpha, -)$ transforms $x_{-\beta}(X^2f)$ into the products of generators of type 2, 1.
Clearly, $S(\alpha, -)$ fixes both generators of type 3. 
As for the remaining generators type 5, \cref{Crels} shows that the corresponding conjugate can be written as a product of generators of type 6, 6, 5. \end{proof}

\begin{corollary} The image of $K(\alpha, \beta)$ under $S(\alpha, -)$ is contained in $P_\beta(0)$. \end{corollary}
\begin{proof} Follows from the above lemma and the fact that the generators of $U$ are generators of the second type for $P_\beta(0)$ in the sense of~\cref{defP0}.
 Indeed, if $\gamma \in Z_+(\alpha) \setminus \{ \alpha - \beta \}$ is such that $\langle \beta, \gamma \rangle = -1$, then $ \langle \alpha - \beta, \gamma \rangle \geq 2$, hence
  $\gamma = \alpha - \beta$, a contradiction. \end{proof}

\begin{lemma} Suppose $g \in K(A[X], M[X])$ then \[S_\alpha(a, g)\cdot  h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-N_{\alpha,-\beta}\cdot m'a) \in P\left(\beta, \frac{m'}{1 + am}\right).\] \end{lemma}
\begin{proof}
 By~\cref{K-a-b} $g = g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$ for some $g_0\in K(\alpha, \beta)$.
 \begin{multline} \nonumber S_\alpha(a, g) = S_\alpha(a, g_0) \cdot S(a, x_{-\alpha}(mX)) \cdot S_\alpha\left(\frac{a}{1+am}, x_{-\beta}(m'X)\right) = \\ = S_\alpha(a, g_0) \cdot \langle -a, m \rangle \cdot h_\alpha(1+am) \cdot x_{-\beta}(m'X) \cdot x_{\alpha-\beta}\left(\frac{N_{\alpha, -\beta} \cdot m'a}{1+am}\right) = \\ =
  S_\alpha(a, g_0) \cdot \langle -a, m \rangle \cdot  x_{-\beta}\left(\frac{m'X}{1+am}\right) \cdot x_{\alpha-\beta}\left(N_{\alpha, -\beta} \cdot m'a\right) \cdot h_\alpha(1+am). \end{multline}
The assertion now follows from the preceding corollary.
\end{proof}

\begin{lemma} For $a \in A$ one has $K(\alpha, \beta)^{x_{\beta - \alpha}(a)} \subseteq K(\alpha, \beta)$. \end{lemma}
\begin{proof}
 By~\eqref{Z2}--\eqref{Z4} of~\cref{Zrels} the conjugate to the generator $g=z_\gamma(Xf, \xi)$ of type 1 by $x_{\beta-\alpha}(a)$ either coincides with $g$ or is a product of elements of type 4, 1, 1.

 Now let $g$ be a generator of type 2 or 3. It is clear that conjugation by $x_{\beta-\alpha}(a)$ either fixes $g$ or transforms it into a product of two elements of type 2 or 3.

 By~\eqref{C1}--\eqref{C3} of~\cref{Crels} the conjugate to a generator $g = c_\delta(f, X\xi)$ of type 5 either coincides with $g$ or is a product of generators of type 5, 4, 1.

 Finally, from~\cref{rem:palpha} we obtain that $z_{\alpha-\beta}(Xf, a) \in K(A[X], M[X]) \cap P_\alpha(0) \cap P_{\beta}(0) = K(\alpha, \beta)$. \end{proof}
